Flattering Advice: Avoiding Disappointment in Advice-Giving

### 2024-12-15 manuscript/manuscript.Rmd
Edits up to study1regs

---
title: "Flattering Advice: Avoiding Disappointment as a Driver of Gender Discrimination"
shorttitle        : "Flattering Advice"
author: 
  - name          : "Amanda Chen"
    affiliation   : "1"
    corresponding : yes    
    email         : "zchengj@connect.ust.hk"
    address       : "Department of Management, The Hong Kong University of Science and Technology, Hong Kong"
  - name          : "David Hagmann"
    affiliation   : "1"
affiliation:
  - id            : "1"
    institution   : "The Hong Kong University of Science and Technology"
note : |
  `r format(Sys.time(), "%e %B, %Y")`
abstract: |
  The primary purpose of advice is often seen as helping recipients make better decisions and solve problems. However, this paper reveals that advisors are also influenced by interpersonal concerns. Specifically, we propose that advisors consider the recipient's "belief utility" and may seek to avoid disappointing them, resulting in what we call "flattering advice." Through three pre-registered experiments involving real interactions between advisors and advisees (n = 3,900), we demonstrate that advisors account for advisees' expectations, even when irrelevant to solving the problem. Specifically, advisors tailor their advice to match advisees' expectations about their own capabilities, aiming to avoid disappointing them (Study 1). Advisors inflate their advice due to interpersonal concerns, with those who care about being liked by the advisee inflating their advice to a greater extent. Advisees, in turn, reward this flattery, perceiving these advisors as more likable and equally trustworthy compared to those who aim to give more accurate advice (Study 2). Additionally, when advisors match advisees' expectations, men tend to receive more aspirational advice than women, due to their higher confidence, even when only expectations (not gender) are visible to the advisor. However, relying on these expectations leads to poorer decision outcomes (Study 3). We conclude by discussing the practical and theoretical implications of our findings, as well as directions for future research.

@@

# Introduction

We frequently seek and offer advice, often with the hope of solving problems 
more effectively. Whether we are navigating personal dilemmas or making 
professional decisions, advice is seen as a valuable tool for improving 
outcomes. For instance, in some studies, participants are asked to estimate 
quantities or choose between lotteries [@Benjamin2015]. Advisors are often 
motivated to provide accurate advice [@Jonas2003], and engage in perspective-taking
to align with the preferences of the advisee [@Kray2000; @Kray1999]. When 
uncertain, they may even prefer that advisees rely less on their recommendations
[@Ache2020]. This suggests that people are generally concerned with offering 
good advice, assuming accuracy is the primary objective.

Indeed, seeking and giving advice often involve complex conversational dynamics 
that can be challenging to manage. People frequently struggle with 
decisions about whom to approach for advice, whether they seek it too 
often or too little, and the potential consequences of asking for advice—or
failing to—when it’s expected [@lee1997;@minson2012;@see2011]. 
From the advisor's perspective, factors such as knowledge and expertise [@sniezek2001],
confidence [@sah2013], age [@zhang2020], and communication style [@yaniv2012]
also play critical roles in determining whether accurate advice is 
effectively conveyed.

While much of the advice literature emphasizes the instrumental value of 
advice—such as improving decision satisfaction or prediction accuracy, assuming
both parties prioritize accuracy—research suggests that solving the problem is 
not the only concern in these interactions. Advice seekers may feel embarrassed 
to ask for help [@Benabou2022] and may avoid seeking advice if they fear the 
information could lead to disappointment [@Gill2012]. Moreover, people tend 
to favor advisors who withhold unpleasant information [@Shalvi2019] and even 
punish those who tell them things they would rather not hear [@John2019] This 
indicates that individuals strategically select advice to shield themselves 
from uncomfortable truths, protecting the positive beliefs they hold about 
themselves and their anticipated future [@Loewenstein2018;
@Loewenstein1987]. But do advice givers recognize and account 
for the emotional cost of delivering honest information to the recipient?

In many real settings, advice often incorporates beliefs about the
recipient. Someone recommending an expensive restaurant conveys that
they think the advisee is wealthy enough to afford an expensive meal,
and someone recommending a student pursue a PhD in economics assumes
that they are intellectually capable. Conversely, telling a poorly
performing student to switch to a less-demanding major conveys a belief
that the student is not capable of improving. Thus, while the painful
truth may prevent someone from making a bad decision, it may come at a
hedonic cost to the recipient and damage the relationship between the
adviser and advisee. We propose that advisers take these costs into
account, even when the interactions are entirely anonymous and they are
incentivized for the quality of the advisee's decision.

Specifically, we focus on the signaling value of advice: what does the
advice imply about the adviser's perception of the advisee? We propose
that advisees have expectations about the advice they receive and treat
this as a reference point [@Koszegi2006]. Advice that falls short of
these expectations creates disappointment, while advice that exceeds
them is flattering and creates positive interpersonal benefits because
it creates a perception that the adviser holds the advisee in high
esteem. Such interpersonal considerations may be as important, if not
more important, to the adviser than the instrumental value of the
advice: the adviser directly experiences a souring relationship, but may
suffer little and only much delayed consequences if an advisee makes a
poor life decision.

Our account therefore predicts that people give and receive advice that
is more flattering and suggestive of inflated ability and optimistic
outcomes than would advice in the absence of such interpersonal
considerations. However, we propose that this is not true for all
advisees equally. Presenting flattering advice requires the formation of
beliefs about the advisee's expectations (reference point). @Exley2022
show that men are more overconfident than women, conditional on equal
performance, and that people anticipate this difference. An adviser who
seeks to avoid disappointment and incorporates expectations into their
advice would then present more favorable advice to male advisees than to
female advisees (see Figure 1 for an illustration). This provides a
novel account for a well-known finding that men receive more
aspirational advice than do women [@Kanze2018]. Notably, when it pays to
have accurate beliefs, such flattering advice would come at a cost:
while men would be more likely to aim higher, they would also suffer
greater costs from aiming too high and failing to meet the objective.

In a large, preregistered experiment (n = 1,200), we demonstrate that 
advisors take into account advisees' expectations, even when those expectations
offer no relevant insights for solving the decision-making problem. 
Advisors were more likely to encourage advisees to compete against strong
competitors when they saw that the advisees had high expectations of their 
own abilities, compared to when the advisees had low expectations. In a second
preregistered experiment (n = 700), we show that advisors respond to interpersonal
incentives, telling advisees they are more attractive than they believe, and 
inflating their advice more when incentivized for likability rather than accuracy.
Notably, they still inflate their advice even when incentivized solely for accuracy.
Advisees, in turn, reward this flattering advice, rating these advisors as more 
likable and no less trustworthy than those who provide more accurate feedback. 
In the third preregistered experiment (n = 2,000), we replicate the finding that
advisors consider advisees' expectations when giving advice. Additionally, we find
that when only expectations (but not gender) are shown, men receive more aspirational
advice than women. This tendency to factor in expectations ultimately leads to poorer
advice, even when advisors are incentivized based on the outcome of the advisee’s 
decision.

@@

# Study 1
In Study 1, we investigate whether givers take into account advisees' expectations 
when providing advice. We compare the advice given to recipients who expressed either
high or low expectations, across two treatments: one where givers were aware of these 
expectations (Expectation treatment) and one where this information was unknown to them 
(Performance treatment).

The experiment consisted of three stages, in which we manipulated advisees' expectations and whether givers had access to this information. First, we measured participants' performance, then informed them that their performance would be compared to that of another participant, with the higher scorer eligible to win a bonus. Participants were asked to choose their competitor from either the top 20 performers ("High Performer Group") or the bottom 20 performers ("Low Performer Group") out of a pool of 50 competitors. We nudged participants to have high or low expectations by encouraging them to compete against either the High Performer Group or the Low Performer Group. Advisors were randomly assigned to one of two treatments: seeing only performance information or both performance and expectation information. We hypothesize that advisees who indicate they are capable of competing against strong competitors will be more likely to receive advice to do so.

As part of our main experiment, participants were asked to choose a group 
of previous participants to compete against. To create these groups, we 
first recruited a sample of  `r scales::comma(dim(study1_ability50)[1])`
participants from Prolific to complete a 10-question ability quiz. The quiz 
included word puzzles, identifying emotions from photos, and selecting the
best responses in given scenarios. These questions were adapted from surveys 
that measure problem-solving, emotional intelligence, and communication
skills. We selected these specific abilities based on a pretest in which 
participants ranked them as the three most critical skills in modern society, 
making performance on this task ego-relevant.Participants had five minutes to 
answer the quiz and were paid 5 cents for each correctly answered question. 
We define the top 20 scorers as the "High Performer Group"
and the bottom 20 scorers as the "Low Performer Group."

We then recruited `r scales::comma(dim(study1_time1)[1])`
participants to serve as advisees in Stage 1 of our main experiment. These 
participants completed the same 10-item ability quiz as the earlier group, 
with the opportunity to earn 5 cents for each correct answer. After the 
quiz, we asked them to indicate their initial preference for competitors. 
Half of the participants were randomly shown the default option of the 
'High Performer Group,' highlighted in blue ("High Default" treatment), while the other half were 
shown the 'Low Performer Group' as the default ("Low Default" treatment). This manipulation was 
designed to influence advisees' expectations, as advisees who believed 
they could compete against stronger competitors were perceived by givers 
to have higher expectations. However, participants were free to opt out 
of the default choice.

We then recruited `r scales::comma(dim(study1_time2_giver)[1])`
participants for Stage 2, placing them in the role of advisers. We began
by informing them of the ability quiz that participants in the
preliminary study and Stage 1 had completed, and informed them of the
average score of all participants in the preliminary study. Advisers had
to recommend whether an advisee should compete against the Low
Performer Group or the High Performer Group (we used these terms in the survey).
We anticipated that being told to compete against High Performers is
more flattering and hence being told to compete against the Low
Performers would be disappointing if one had expected to do well.
Advisees would earn 20 cents if their score was equal to or higher than
a randomly selected member of the Low Performer Group and they chose to
compete against this group, or 50 cents if they performed as well or
better than a randomly selected member of the High Performer Group and
they chose to compete against that group. If they scored lower, they
would not receive any bonus.

Advisers were randomly assigned to one of two treatments. In the
"Performance" treatment, they only observed the score of the advisee on the
ability quiz. In the "Expectation" treatment, they observed the
score as well as the advisee's initial preference for which group to compete against.
However, since the outcome was based solely on the quiz score and advisees didn’t 
know their scores, their initial choice wasn’t useful in deciding which group had a 
higher expected bonus. Advisers gave recommendations to 10 advisees and were told that 
if their advice was used by a participant in a follow-up survey, they would receive 
the same bonus as that participant. The survey concluded with basic demographic 
questions.

Finally, we invited participants from Stage 1 back for the follow-up
survey. Following our preregistration, we kept the survey open for 7
days. In total, `r scales::comma(dim(study1_time3)[1])` participants
(`r scales::comma(dim(study1_time3[study1_time3$Gender == 'Male',])[1])`
men,
`r scales::comma(dim(study1_time3[study1_time3$Gender == 'Female',])[1])`
women) returned. The brief survey reminded them of the task they
completed in Stage 1, informed them that other participants from
Prolific had observed their real score and given them advice against
which group to compete against, and finally were reminded them of how
many questions they guessed they had answered correctly. Importantly,
they were not informed of their true score or the score of the groups
they could compete against. Participants then observed the advice from a
randomly selected adviser and made their decision.

@@

<!-- Amanda: Wondering if we need to report the p-value of priming manipulation -->

@@

We begin by examining the performance of the Stage 1 participants.
Because our treatment takes place after participants completed the
ability quiz, we would not expect a difference in performance across
the Low and High Default treatments. Indeed, the two groups scored
no different from one another
(`r round(mean(study1_time1[study1_time1$default == "Low",]$Score),2)`
and
`r round(mean(study1_time1[study1_time1$default == "High",]$Score),2)`
for the Low Defult and High Defult treatments, respectively,
`r papaja::apa_print(t.test(Score ~ default, data = study1_time1, var.equal = T))$statistic`).
The priming did, however, affect advisees' initial choices. In the "Low Default" treatment, 
only `r round(mean(study1_time1[study1_time1$default == "Low",]$Guess),2)*100`% 
of participants initially preferred competing against the High Performer Group, 
compared to `r round(mean(study1_time1[study1_time1$default == "High",]$Guess),2)*100`%
of participants who saw the High Performer Group highlighted ($\chi^2$(1, n = 201) = 36.62, p < .001).

<!-- No main interactive effect on expected bonus, therefore I did not include it in this tabel -->

@@

# Fit the two models
model1 <- lm(Advice ~ ExpShow * Treatment, data = study1_advice)
model2 <- lm(Advice ~ Treatment + Score, data = study1_advice %>% dplyr::filter(ExpShow == 1))

# Use sandwich package for clustered standard errors
library(sandwich)

# Clustered standard errors by GiverID
vcov_list <- list(sandwich::vcovCL(model1, cluster = ~GiverID), 
                  sandwich::vcovCL(model2, cluster = ~GiverID))

modelsummary::modelsummary(
  list(`(1)` = model1, `(2)` = model2),
  vcov = vcov_list,
  coef_map = c(
    "TreatmentHigh" = "High Default",
    "ExpShow" = "Expectation Shown",
    "ExpShow:TreatmentHigh" = "Expectation x High Default",
    "Score" = "Performance",
    "(Intercept)" = "Constant"
  ),
  stars = TRUE,
  gof_map = list(list('raw' = 'nobs', 'clean' = 'N', 'fmt' = 0)),
  caption = "Column 1 displays the advice given to compete against a High Performer Group based on whether the advisees were primed with low or high default and the initial preference shown to the advisor. Column 2 displays the advice given to compete against a High Performer Group based on the default and advisees' performance when their initial preference was visible to the advisor. All standard errors are clustered at the level of the advisor."
)

@@

Next, we examine whether advisers took the advisees' expectations into account. 
Recall that advisees who defaulted to competing against the High Performer 
Group were indeed more likely to choose this group, which, from the advisers' 
perspective, could signal high confidence in their abilities. Our theory 
predicts that showing expectations should lead to more flattering advice—
specifically, a recommendation to compete against the High Performer Group—
for advisees with a high default choice compared to those with a low 
default choice. Column 1 of Table \@ref(tab:study1regs) reports a linear
probability model with advice to compete against the high group
as the outcome measure, incorporating the default choice advisees saw, whether expectations
were shown to the adviser, and the interaction of the two. Because each adviser made ten
recommendations, we cluster standard errors at the adviser level.
As predicted, we find a marginally significant interaction effect: advisees 
with a default choice to compete against the High Performer Group (nudged 
to have high expectations, though not necessarily holding them) were more 
likely to receive advice to compete against stronger competitors when 
their expectations were shown compared to when they were hidden.
We reported a linear probability model on advising to compete against the High Performer
group for advisers in the "Expectations" treatment, controlling for the
true performance of the advisee in Column 2 of Table \@ref(tab:study1regs).
We observe a significant main effect of the default treatment, where a high default
increased the likelihood of receiving flattering advice. It is worth noting that, 
since only `r round(mean(study1_time1[study1_time1$default == "High",]$Guess),2)*100`
% of advisees in the high default group actually stuck with their default 
choice, this represents a conservative test of the effect of high expectations on 
the likelihood of receiving flattering advice.

>>>>

---
title: "Flattering Advice: Avoiding Disappointment in Advice-Giving"
shorttitle        : "Flattering Advice"
author: 
  - name          : "Amanda Chen"
    affiliation   : "1"
    corresponding : yes    
    email         : "zchengj@connect.ust.hk"
    address       : "Department of Management, The Hong Kong University of Science and Technology, Hong Kong"
  - name          : "David Hagmann"
    affiliation   : "1"
affiliation:
  - id            : "1"
    institution   : "The Hong Kong University of Science and Technology"
note : |
  `r format(Sys.time(), "%e %B, %Y")`
abstract: |
  Good advice improves decision quality but often requires delivering unpleasant truths that may disappoint advisees. Across three pre-registered and incentivized experiments involving real adviser-advisee interactions (n = 3,900), we demonstrate that advisers prioritize avoiding disappointment, even at the expense of accuracy. In Study 1, advisers financially rewarded for accuracy still tailored recommendations to aspirational goals expressed by advisees, resulting in poorer advice. When incentivized to be liked, advisers provided even more flattering advice, and advisees rated these advisers as more likable, despite the advice being less honest and less accurate (Study 2). In Study 3, advisers incorporated advisees' subjective and uninformative performance expectations into recommendations, leading to systematically different advice for men and women. Because men expected to perform better than women, they received more aspirational advice, even when their gender was unknown to advisers. Advisers' efforts to avoid disappointment may thus contribute to systematic gender disparities in advice, with implications for downstream decision-making and equity.

@@

# Introduction
Advice plays a critical role in both professional and personal decision-making, 
often serving as a crucial tool for navigating complex challenges and improving 
outcomes [@Gino2007; @Harvey1997; @Soll2009]. While prior research has 
extensively examined the *recipients* of advice (e.g., how they evaluate or act 
on recommendations) far less attention has been devoted to understanding the 
motivations and behaviors of the *givers* of advice. In this paper, we shift the 
focus to advisers, proposing that their recommendations are shaped not only by 
accuracy considerations but also by interpersonal concerns. Specifically, we 
propose that advisers factor in advisees' subjective expectations, providing 
flattering advice that aligns with these expectations, even when doing so leads 
to objectively worse recommendations. Notably, this tendency persists in our 
experimental settings, where advisees' expectations are clearly uninformative 
and advisers are financially incentivized for accuracy.

Advice is often viewed as a mechanism to improve decision satisfaction or 
prediction accuracy, assuming both parties prioritize solving the problem at 
hand. However, prior research highlights that interpersonal dynamics can 
complicate these interactions. Advice seekers may avoid asking for help due to 
fear of rejection [@Benabou2022], and people generally have been shown to avoid
information that could lead to disappointment [@Gill2012; @Golman2017]. 
They are motivated to avoid unpleasant truths in an ethical dilemma [@Shalvi2019] 
and dislike those who deliver unwelcome feedback even when they had no role in
the outcome [@John2019]. These tendencies align with models of belief utility 
[@Loewenstein2018], which suggest that individuals experience 
hedonic costs when receiving bad news. A natural reference point for evaluating 
the valence of advice is the advisee's expectation in the absence of advice
[@Koszegi2006]. Consequently, advisers who are aware of expectations may 
strategically adapt their advice to avoid delivering bad news, even at the 
expense of accuracy.

This interpersonal dimension of advice-giving has significant implications for 
understanding systematic gender differences in advice quality. Men are more 
likely than women to receive aspirational advice and encouragement to pursue 
competitive or risky opportunities [@Kanze2018]. Conversely, women are often 
shielded from criticism [@Jampol2023], which, while intended to be kind, 
may ultimately limit their professional growth. We propose a novel mechanism to 
explain these patterns: advisers calibrate their recommendations to match 
advisees’ expectations. Because, in many tasks (including those in our experiments)
men are more confident and have higher expectations about their performance than
do women, they are more likely to receive flattering (but, in our setting, worse) 
advice.

We present evidence for this mechanism from three preregistered and incentivized 
experiments involving real interactions between advisers and advisees (N = 3,900). 
In Study 1, we experimentally manipulate advisee's expectations and show
that advisers account for those expectations, even when they offer no relevant
insight for the decision. In Study 2, we show that advisers put more weight on
interpersonal concerns when they are incentivized to be liked. Advisees reward
this flattery by rating advisers as more likeable and equally trustworthy compared
to those offering more honest (and accurate) feedback. In Study 3, we measure
expected performance on a math quiz and show that advisers take these expectations
into account even when they have information about actual performance. Because
men expect to score higher, they are more likely to be advised to compete against
a stronger group for a higher potential payment than are women, even when advisers
are unaware of the advisees' gender. Notably, this leads to worse advice for men.

@@

# Study 1
We first examine whether advisers take into account the expectations of advisees
when providing a recommendation. A group of participants ("Advisees") complete 
a quiz consisting of ten questions that draw on ego-relevant domains. They then
express a non-binding preference to compete against a group of high performers
or low performers on the same task, based on their past performance. We nudge
participants towards picking either the low or the high performer group by 
selecting one of the two by default. A second group of participants ("Advisers") 
observe Advisees' score on the quiz and, in one treatment, also which group
they had selected. We predicted that Advisees who were nudged toward the high
performer group would be more likely to receive advice to compete against this
high group when Advisers observed their non-binding choice.

## Methods
In a preliminary stage, we recruited `r scales::comma(dim(study1_ability50)[1])` 
participants from Prolific and gave them five minutes to complete a quiz 
consisting of ten items. The quiz included word puzzles,
identifying emotions from photos, and selecting the best responses for hypothetical
scenarios. These questions were adapted from surveys that measure problem-solving,
emotional intelligence, and communication skills---which we pre-tested as being
important in modern society and hence where participants might have a stake in
doing well. Participants received a bonus of five cents for each correctly
answered question. We then ranked them based on their score and label the 20
participants with the lowest (highest) scores as the Low (High) Performer Group.

Next, we recruited `r scales::comma(dim(study1_time1)[1])` participants who
completed the same 10-item quiz, also earning five cents for each correct answer.
We then asked them to express a non-binding preference for whether they would
like to compete against the High or Low Performer Group. We informed them that
they would be invited back at a later date when they could make a binding decision
and they could earn a bonus based on whether their score on this quiz was equal
to or higher than a randomly selected member from their comparison group.
If they picked the High Performer Group and had an equal or higher score than
a randomly selected member of that group, they would earn a bonus of 50 cents.
If they picked the Low Performer Group, they could earn a bonus of 20 cents.
If their score was lower in this comparison, they would not earn an additional
bonus. We randomized which of the two groups (High or Low Performers) was 
selected by default, and participants were free to select the other group.
Participants also made a guess as to their score, and the survey concluded with 
basic demographic questions.

We then recruited `r scales::comma(dim(study1_time2_giver)[1])`
participants for the role of advisers, and the focal part of our experiment. 
They were informed of the ability quiz that participants had completed, how the 
Low Performer Group and High Performer Groups were constructed, as well as the
choice and incentives for the other participants. We then asked participants
to give advice to ten participants on which group they should compete against.
Advisers were randomly assigned to one of two treatments. In the
"Performance" treatment, they observed the score of the other participant.
In the "Performance + Expectation" treatment, they additionally observed the
advisee's non-binding choice for which group to compete against.
However, since the outcome was based solely on the past quiz score and advisers,
but not advisees, know the score, this initial choice was not informative.
Advisers could earn the same bonus as one of the participants they had given
advice to and who returned to make a decision. The survey concluded with basic 
demographic questions.

Finally, we invited advisees back for the follow-up survey. Following our 
preregistration, we kept the survey open for 7
days. In total, `r scales::comma(dim(study1_time3)[1])` participants
returned. The short survey reminded them of the task they
completed in the previous survey, informed them that other participants from
Prolific had observed their real score and given them advice against
which group to compete against, and finally reminded them of how
many questions they guessed they had answered correctly. Importantly,
they were not informed of their true score or the score of the groups
they could compete against. Participants then observed the advice from a
randomly selected adviser and made their decision.

@@

@@

We begin by examining the performance of the Stage 1 participants.
Because our default treatment takes place after participants completed the
ability quiz, we do not expect a difference in performance across
the Low and High Default treatments. Indeed, the two groups scored
no different from one another
(`r round(mean(study1_time1[study1_time1$default == "Low",]$Score),2)`
and
`r round(mean(study1_time1[study1_time1$default == "High",]$Score),2)`
for the Low Default and High Default treatments, respectively,
`r papaja::apa_print(t.test(Score ~ default, data = study1_time1, var.equal = T))$statistic`).
The default manipulation affected their initial choices. In the "Low Default" treatment, 
only `r round(mean(study1_time1[study1_time1$default == "Low",]$Guess),2)*100`% 
of participants initially preferred competing against the High Performer Group, 
compared to `r round(mean(study1_time1[study1_time1$default == "High",]$Guess),2)*100`%
of participants who saw the High Performer Group highlighted ($\chi^2$(1, n = 201) = 36.62, p < .001).

@@

modelsummary::modelsummary(
  list(`(1)` = lm(Advice ~ ExpShow * Treatment, data = study1_advice), 
       `(2)` = lm(Advice ~ Treatment + Score, data = study1_advice %>% dplyr::filter(ExpShow == 1))),
  vcov = ~GiverID,
  coef_map = c(
    "TreatmentHigh" = "High Default",
    "ExpShow" = "Expectation Shown",
    "ExpShow:TreatmentHigh" = "Expectation x High Default",
    "Score" = "Performance",
    "(Intercept)" = "Constant"
  ),
  stars = TRUE,
  gof_map = list(list('raw' = 'nobs', 'clean' = 'N', 'fmt' = 0)),
  caption = "Advice to compete against the High Performer Group in Study 1. Displaying the non-binding choice of those for whom the Low Performer Group was selected by default makes it more likely that they are advised to compete against the High Performer Group (Column 1). Column 2 restricts the analysis to advisers who observed advisees' initial non-binding choice and controls for advisees' score on the quiz. Standard errors are clustered at the adviser level."
)

@@

We now examine whether advisers took the advisees' expectations into account. 
Recall that advisees who were defaulted to competing against the High Performer 
Group were indeed more likely to choose this group, which, from the advisers' 
perspective, could signal high confidence in their abilities. Our theory 
predicts that showing expectations should lead to more flattering advice—
specifically, a recommendation to compete against the High Performer Group—
for advisees with a high default choice compared to those with a low 
default choice. Column 1 of Table \@ref(tab:study1regs) reports a linear
probability model with advice to compete against the high group
as the outcome measure, incorporating the default choice advisees saw, whether expectations
were shown to the adviser, and the interaction of the two. Because each adviser made ten
recommendations, we cluster standard errors at the adviser level.
As predicted, we find a marginally significant interaction effect: advisees 
with a default choice to compete against the High Performer Group (nudged 
to have high expectations, though not necessarily holding them) were more 
likely to receive advice to compete against stronger competitors when 
their expectations were shown compared to when they were hidden.
We reported a linear probability model on advising to compete against the High Performer
group for advisers in the "Expectations" treatment, controlling for the
true performance of the advisee in Column 2 of Table \@ref(tab:study1regs).
We observe a significant main effect of the default treatment, where a high default
increased the likelihood of receiving flattering advice. It is worth noting that, 
since only `r round(mean(study1_time1[study1_time1$default == "High",]$Guess),2)*100`
% of advisees in the high default group actually stuck with their default 
choice, this represents a conservative test of the effect of high expectations on 
the likelihood of receiving flattering advice.
